Title Goes Here

### 2017-08-17 analysis/paper/paper.Rmd
results of email survey

# overall rate of response
emails_out <- sum(!is.na(email_survey$`email sent date`))
emails_back <- sum(!is.na(email_survey$`response received date`))
email_response_rate <- round(emails_back / emails_out, 1) * 100
data_items_received <-  sum(!is.na(email_survey$`content recieved date`))
```

Our sample focused on _Journal of Archaeological Science_ articles on experiments with stone artefacts that were published during `r min(email_survey$'publication year', na.rm = TRUE)` and `r max(email_survey$'publication year', na.rm = TRUE)`. We focused on stone artefact experiments because the all research materials are generated by the researcher so there are not other stakeholders to consider what determining how to share the data. There are also no risks of damage to people or property in sharing these data because they do not include archaeological sites or human subjects. We requested the datasets for use

We sent out `r emails_out` emails to authors of these papers, and received `r emails_back`, a `r email_response_rate`% response rate. We revieced

>>>>

# overall rate of response
emails_out <- sum(!is.na(email_survey$`email sent date`))
emails_back <- sum(!is.na(email_survey$`response received date`))
email_response_rate <- round(emails_back / emails_out, 1) * 100
data_items_received <-  sum(!is.na(email_survey$`content recieved date`))
sharing_rate <-  round(data_items_received / emails_out, 1) * 100
```

We conducted a pilot study to explore data sharing in archaeology. Our sample focused on _Journal of Archaeological Science_ articles on experiments with stone artefacts that were published during `r min(email_survey$'publication year', na.rm = TRUE)` and `r max(email_survey$'publication year', na.rm = TRUE)`. We focused on stone artefact experiments because the all research materials are generated by the researcher so there are not other stakeholders to consider when determining how to share the data: the researcher has complete control over the data. There are also no risks of damage to people or property in sharing these data because they do not include archaeological sites or human subjects. In contacting the authors, we requested the datasets for use in a graduate seminar with the aim of reproducing the published results and further exploring the data (this stage is still in progress). We promised to contact the authors if we discovered anything new, and not to share the data further without their permission.

We sent out `r emails_out` emails to authors of these papers, and received `r emails_back`, resulting in a `r email_response_rate`% response rate. We recieved `r data_items_received` responses that included data files, giving an overall sharing rate of `r sharing_rate`%. Wi

change over time...

location...
student or not...
